---
title: "Final"
output: 
  flexdashboard::flex_dashboard:
   theme: simplex
runtime: shiny
---


```{r setup, include=FALSE}
if(!require("pacman")) install.packages("pacman")
p_load(wordcloud, ggraph, igraph, Rmisc, scales, tidytext, text2vec, stopwords, Matrix, tokenizers, knitr, keras, tensorflow, magrittr, tidyverse, caret, flexdashboard, shiny, rmarkdown, Hmisc, DT, data.table, viridis, leaflet.extras, htmltools, leaflet, jsonlite, rjson, syuzhet, reticulate, glue, tm)
import("pickle")
import("keras")
import("numpy")

assignInNamespace("cedta.override", c(data.table:::cedta.override,"rmarkdown"), "data.table")

opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)
review<-fread("/Users/11kolop/Desktop/Final Submission/rev")


```

```{r read_data, include=FALSE}
tokens <- readRDS("/Users/11kolop/Desktop/Final Submission/tokens.RData")
bitokens <- readRDS("/Users/11kolop/Desktop/Final Submission/bigrams.RData")
br<-readRDS("/Users/11kolop/Desktop/Final Submission/business_restaurants")

tokens$Target <- ifelse(tokens$stars > 3, "Positive", "Negative")
bitokens$Target <- ifelse(bitokens$stars > 3, "Positive", "Negative")
```


```{r constant}
cities <- names(sort(table(tokens$city), decreasing = TRUE))
```

```{r functions}
##https://www.cnn.com/travel/article/world-best-food-cultures/index.html
us.type<-grepl("United States|American", br$categories)
us<-br[us.type,]
us$categories<-"American"
mex.type<-grepl("Mexico|Mexican", br$categories)
mex<-br[mex.type,]
mex$categories<-"Mexican"

thai.type<-grepl("Thailand|Thai", br$categories)
thai<-br[thai.type,]
thai$categories<-"Thai"

gre.type<-grepl("Greece|Greek", br$categories)
gre<-br[gre.type,] 
gre$categories<-"Greece"

indi.type<-grepl("India|Indian", br$categories)
indi<-br[indi.type,] 
indi$categories<-"Indian"

jp.type<-grepl("Japan|Japanese", br$categories)
jp<-br[jp.type,] 
jp$categories<-"Japanese"

spain.type<-grepl("Spain|Spanish", br$categorie)
sp<-br[spain.type,]
sp$categories<-"Spanish"

fr.type<-grepl("France|French", br$categorie)
fr<-br[fr.type,]
fr$categories<-"French"

cn.type<-grepl("China|Chinese", br$categorie)
cn<-br[cn.type,]
cn$categories<-"Chinese"

it.type<-grepl("Italy|Italian", br$categorie)
it<-br[it.type,]
it$categories<-"Italian"

ca.type<-grepl("Caribbean", br$categorie)
ca<-br[ca.type,]
ca$categories<-"Caribbean"

med.type<-grepl("Mediterranean", br$categorie)
med<-br[med.type,]
med$categories<-"Mediterranean"

vt.type<-grepl("Vietnamese", br$categories)
vt<-br[vt.type,]
vt$categories<-"Vietnamese"

rest<-data.table(rbind(us,mex,thai,gre,indi,jp,sp,fr,cn,it,ca,med,vt))
setorderv(rest, cols = "stars", order = -1) 
```

```{r constants}
state.name<-"state"
stars.name<-"stars"
city.name<-"city"
category.name<-"categories"
unique.state <- rest[, unique(get(state.name))]
#unique.city <- rest[, unique(get(city.name))]
unique.city <-names(sort(table(rest$city), decreasing = T))
unique.type <- rest[, unique(get(category.name ))]
```



Clustering Map
=====================================  


Row {data-height=800}
-------------------------------------

```{r,fig.height=10, fig.width=19}

br %>% 
  leaflet() %>% 
  addTiles() %>%
  addCircleMarkers(radius = 2, label = ~htmlEscape(`name`),
                         clusterOptions = markerClusterOptions()) 

```

Star Rating Distribution
===================================


Row {data-height=500,.bgred}
-------------------------------------

```{r respondents}
inputPanel(
  
  selectInput(inputId="city", label = "Select City:", choices = unique.city, selected = unique.city[1]),
  selectInput(inputId="category", label = "Select Category:", choices = unique.type, selected = unique.type[1]),
  
  checkboxInput(inputId = "product_info_decreasing2", label = "Sorted", value=TRUE),
  checkboxInput(inputId = "product_info_show_percentages2", label = "Show Percentages", 
                value = TRUE),
  sliderInput(inputId = "product_info_names_magnification2", label = "Magnify Star Names",
              min = 0.4, max = 1.4, value = 1, step = 0.1)
)


renderPlot({

  count<-rest[get(category.name)%in%input$category& get(city.name)%in%input$city, .N, by=stars]
   rates<-count[, star.rates := 100 * N/sum(N)]
   

   
  if(input$product_info_decreasing2 == TRUE){
    setorderv(x = rates, cols = "star.rates", order = -1)
  }  
  barplot(height = rates[, star.rates], 
          names.arg = rates[, get(stars.name)], 
          space=0.01, las = 1, main = input$category, 
          ylab = "Star Rating Percentage", 
          cex.names = input$product_info_names_magnification2, 
          ylim = c(-15, 100), xaxt = "n", axes = F, col = "red2")
  axis(side = 2, at = 20*(0:5), las = 2)
  
  text(x = -0.5 + 1.02*1:rates[, .N], y = -5, 
       labels = rates[, get(stars.name)], srt = 45, 
       cex = input$product_info_names_magnification2, pos = 2)
  
  if(input$product_info_show_percentages2 == TRUE){
    space_val = 0
    text(x = -0.4 + 1:rates[, .N] * (1+space_val), 
         y = rates[, star.rates], 
         labels = sprintf("%.2f%%", rates[, star.rates]), pos = 3)
  }
})
```

Top Restaurants
=====================================  



Row {data-height=800}
-------------------------------------
```{r,}
inputPanel(
  
  selectInput(inputId="city.top", label = "Select City:", choices = unique.city, selected = unique.city[1]),
  selectInput(inputId="category.top", label = "Select Category:", choices = unique.type, selected = unique.type[1]),
  checkboxInput(inputId = "review.top", label = "Sort by Reviews", value = FALSE),
  sliderInput(inputId = "product_info_number.top", label = "Show Top Restaurant", 
              min = 0, max = 20, value = 20, step = 1)
)

renderTable({
  options = list(autoWidth = FALSE)
  rest.top<-rest
  rest.top<-rest.top[with(rest.top, order(-stars,-review_count))]
  w<-rest.top[get(city.name)%in%input$city.top &get(category.name)%in%input$category.top][1:input$product_info_number.top]
  if (input$review.top == TRUE){
    setorderv(w, cols = "review_count", order = -1)
  }
  data.table(w[,c("name","address", "city","state","postal_code","stars","review_count")])

})
```




Wordcloud
============

```{r cloud}
inputPanel(
    selectInput(inputId = "cloud_city", label = "Choose City", choices = cities, selected = cities[1], multiple = TRUE),
    selectInput(inputId = "cloud_stars", label = "Number of Stars", choices = c(1:5), selected = c(1:5), multiple = TRUE),
    sliderInput(inputId = "cloud_num", label = "Number of Words", min = 1, max = 300, value = 100, step = 1),
    textInput(inputId = "cloud_text", label = "Input Categories")
)

renderPlot({
  cloud_counts <- tokens[grepl(input$cloud_text, tokens$categories)]

  cloud_counts <- cloud_counts[city %in% input$cloud_city & stars %in% input$cloud_stars]
  cloud_counts <- cloud_counts %>% 
  count(word, sort = TRUE) %>% 
  top_n(input$cloud_num, n)
  
  wordcloud(cloud_counts$word, cloud_counts$n, random.order = FALSE, colors = RColorBrewer::brewer.pal(8,"Dark2"), scale = c(8, 0.3))
})
```



Frequency of the Words
=========

Row {data-height=100}
-------------------------------------

```{r warning = FALSE}
inputPanel(
    selectInput(inputId = "freq_city", label = "Choose City", choices = cities, selected = cities[1], multiple = TRUE),
    selectInput(inputId = "freq_stars", label = "Number of Stars", choices = c(1:5), selected = c(1:5), multiple = TRUE)
)

renderPlot({
  freq_counts <- tokens[city %in% input$freq_city & stars %in% input$freq_stars]
  freq_counts %>% 
  group_by(Target) %>% 
  count(word, sort = TRUE) %>% 
  left_join(tokens %>% 
              group_by(Target) %>% 
              summarise(total = n()), by = "Target") %>%
  mutate(freq = n/total) %>% 
  select(Target, word, freq) %>% 
  spread(Target, freq) %>%
  arrange(`Positive`, `Negative`) %>% 
  ggplot(aes(`Positive`, `Negative`)) +
  geom_jitter(alpha = 0.05, size = 0.5, width = 0.25, height = 0.25) +
  geom_abline(color = "red") +
  geom_text(aes(label = word), check_overlap = TRUE) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  labs(x = "Positive", y = "Negative") +
  theme_minimal()
})
```


Bigram WordCloud
=====================================

```{r}
inputPanel(
    selectInput(inputId = "bi_city", label = "Choose City", choices = cities, selected = cities[1], multiple = TRUE),
    selectInput(inputId = "bi_stars", label = "Number of Stars", choices = c(1:5), selected = c(1:5), multiple = TRUE),
    sliderInput(inputId = "bi_num", label = "Number of Words", min = 1, max = 300, value = 100, step = 1),
    textInput(inputId = "bi_text", label = "Input Categories")
)

renderPlot({
  bi_counts <- bitokens[grepl(input$bi_text, bitokens$categories)]

  bi_counts <- bi_counts[city %in% input$bi_city & stars %in% input$bi_stars]
  bi_counts <- bi_counts %>% 
  count(bigram, sort = TRUE) %>% 
  top_n(input$bi_num, n)
  
  wordcloud(bi_counts$bigram, bi_counts$n, random.order = FALSE, colors = RColorBrewer::brewer.pal(8,"Dark2"), scale = c(7, 0.3))
})
```


Bigram Frequency
===================

Row {data-height=100}
-------------------------------------

```{r warning = FALSE}
inputPanel(
    selectInput(inputId = "freqbi_city", label = "Choose City", choices = cities, selected = cities[1], multiple = TRUE),
    selectInput(inputId = "freqbi_stars", label = "Number of Stars", choices = c(1:5), selected = c(1:5), multiple = TRUE)
)

renderPlot({
  freqbi_counts <- bitokens[city %in% input$freqbi_city & stars %in% input$freqbi_stars]
  freqbi_counts %>% 
  group_by(Target) %>% 
  count(bigram, sort = TRUE) %>% 
  left_join(bitokens %>% 
              group_by(Target) %>% 
              summarise(total = n()), by = "Target") %>%
  mutate(freq = n/total) %>% 
  select(Target, bigram, freq) %>% 
  spread(Target, freq) %>%
  arrange(`Positive`, `Negative`) %>% 
  ggplot(aes(`Positive`, `Negative`)) +
  geom_jitter(alpha = 0.05, size = 0.5, width = 0.25, height = 0.25) +
  geom_abline(color = "red") +
  geom_text(aes(label = bigram), check_overlap = TRUE) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  labs(x = "Positive", y = "Negative") +
  theme_minimal()
})
```

Sentiment Analysis
=====================================  

Row {data-height=500}
-------------------------------------

```{r}
inputPanel(
  selectInput(inputId="SS", label = " Star Level", choices = c(1:5), selected = c(1:5)[1]))


renderPlot({
mydata <- Corpus(VectorSource(review[review$stars==input$SS,]$text))
mydata <- tm_map(mydata, content_transformer(tolower))
removeNumPunct <- function(x) gsub("[^[:alpha:][:space:]]*", "", x)
mydata <- tm_map(mydata, content_transformer(removeNumPunct))
mydata <- tm_map(mydata, removeWords, stopwords("english"))
mydata <- tm_map(mydata, stripWhitespace)
mydata <- tm_map(mydata, removeNumbers)
mydata <- tm_map(mydata, removePunctuation)

d<-get_nrc_sentiment(as.character(mydata))
td<-data.frame(t(d))
td_new <- data.frame(rowSums(td))
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
qplot(sentiment, data=td_new[1:7,], weight=count, geom="bar",fill=sentiment)+ggtitle("Sentiments")
})
```


Review Prediction
===================================


Row {data-height=500}
-------------------------------------

```{r}
textAreaInput("text", label = h3("Place Review Here"), width = '1500px', height = '300px')
actionButton("submit", "Submit")
v <- reactiveValues()
renderUI(v[["py_chunk"]])
observeEvent(
  input$submit,
  {
    var <- input$text
py_code <- c(
       "```{python, echo=F}",
      "import pickle",
      "from keras.models import load_model",
      "from keras.preprocessing.sequence import pad_sequences",
      "from keras.preprocessing.text import Tokenizer",
      "import numpy as np",
      "revi = str(r.var)",
      "model = load_model('/Users/11kolop/Desktop/Final Submission/my_model.h5')",
      "with open('/Users/11kolop/Desktop/Final Submission/tokenizer.pickle', 'rb') as handle:
      tokenizer = pickle.load(handle)",
      "revi = np.expand_dims(revi, axis=0)",
      "revi = tokenizer.texts_to_sequences(revi)",
      "revi = pad_sequences(revi,maxlen=200)",
      "revi = model.predict([revi], batch_size=1, verbose = 0).argmax()+1",
      "print(revi)",
      "```"
    )
    v[["py_chunk"]] <-HTML(knit(text = py_code))})
```

