---
title: "Homework 2"
author: "Hanao Li"
date: "February 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


####Question 1
```{r}
library(data.table)
setwd("C:/Users/36576/Desktop/gr5243")
data <- fread('Homework 2 Data.csv')
dim(data)
length(unique(data$id))
colnames(data)
```
There are `r dim(data)[1]` rows, `r dim(data)[2]` columns and `r length(unique(data$id))` unique patients. All of the column names mathc up with the description of the data set.


####Question 2
```{r}
#Correct Death Time
data[death == 1, begin:= as.integer(end - 1)]

###Check Begin
class(data$begin)
#Begin < 0
data[begin < 0, .N]
#Begin > End
data[begin >= end, .N]

###Check End
class(data$end)
#End < 0
data[end < 0, .N]

###Check Unique Baseline
data[begin ==0, .(length(unique(id)))]
```
Begin and End looks okay

```{r}
###Check Age
class(data$age)
summary(data$age)
```
Age looks okay

```{r}
###Check diabetes
class(data$diabetes)
summary(data$diabetes)
```
Diabetes looks okay

```{r}
###Check hypertension
class(data$hypertension)
summary(data$hypertension)
```
Hypertension looks okay

```{r}
###Check kidney_disease
class(data$kidney_disease)
summary(data$kidney_disease)
```
Kidney disease looks okay

```{r}
###check Ace
class(data$ace)
summary(data$ace)
```

```{r}
###Check BB
class(data$beta.blocker)
table(data$beta.blocker)
```
Beta blocker looks not okay. We will change "Filled, Picked up, True, Utilized, yeah, yes, Yes" to 1", "didn't take, False, N, no, No, nope, Not filled" to 0

```{r}
data[data$beta.blocker == "didn't take", ]$beta.blocker <- "0"
data[data$beta.blocker == "False", ]$beta.blocker <- "0"
data[data$beta.blocker == "N", ]$beta.blocker <- "0"
data[data$beta.blocker == "no", ]$beta.blocker <- "0"
data[data$beta.blocker == "No", ]$beta.blocker <- "0"
data[data$beta.blocker == "nope", ]$beta.blocker <- "0"
data[data$beta.blocker == "Not filled", ]$beta.blocker <- "0"
data$beta.blocker <- as.integer(data$beta.blocker)
data[is.na(data$beta.blocker), ]$beta.blocker <- 1
summary(data$beta.blocker)
```
Beta blocker looks okay now

```{r}
###Check Statin
class(data$statin)
table(data$statin)
```
Statin looks not okay. Since we don't know whether the patients take the medicine, we will change those non 0, 1s to NA

```{r}
data$statin <- as.integer(data$statin)
summary(data$statin)
```
Statin looks okay now

```{r}
###Check Hospital
class(data$hospital)
summary(data$hospital)
```
Hospital looks okay

```{r}
###Check Heart Attack
class(data$heart.attack)
summary(data$heart.attack)
```
Heart Attack looks okay

```{r}
###Check Death
class(data$death)
summary(data$death)
```
Death looks okay

####Question 3
```{r}
library(DT)
Summaries <- c("Age", "Diabetes", "Hypertension", "Kidney_Disease")
Average <- round(unlist(c(data[begin == 0, .(mean(age))], data[begin == 0, .(mean(diabetes))]*100, data[begin == 0, .(mean(hypertension))]*100, data[begin == 0, .(mean(kidney_disease))]*100)), 1)
Average <- c(Average[1], paste(Average[2:4], c("%")))
Std <- round(unlist(c(data[begin == 0, .(sd(age))], data[begin == 0, .(sd(diabetes))]*100, data[begin == 0, .(sd(hypertension))]*100, data[begin == 0, .(sd(kidney_disease))]*100)), 1)
Std <- c(Std[1], paste(Std[2:4], c("%")))
patientsummary <- data.table(Summaries, Average, Std)
datatable(patientsummary)
```


####Question 4
```{r}
#Heart Attack
data[heart.attack == 1, .N]

#Death
data[death == 1, .N]

#Hosptial
data[, .(sum(diff(hospital) > 0))]

#Number of Rows with Hospital
data[hospital == 1, .N]
```
As we can see here the difference is `r data[hospital == 1, .N] - data[, .(sum(diff(hospital) > 0))]` between the number of rows with hospital and hospital records.


####Question 5
```{r}
#Death
Death <- unlist(c(data[ace == 1, .(sum(death))], data[ace == 0, .(sum(death))], data[beta.blocker == 1, .(sum(death))], data[beta.blocker == 0, .(sum(death))], data[statin == 1, .(sum(death))], data[statin == 0, .(sum(death))]))
#Heart Attack
Heart_Attack <- unlist(c(data[ace == 1, .(sum(heart.attack))], data[ace == 0, .(sum(heart.attack))], data[beta.blocker == 1, .(sum(heart.attack))], data[beta.blocker == 0, .(sum(heart.attack))], data[statin == 1, .(sum(heart.attack))], data[statin == 0, .(sum(heart.attack))]))
##Hospitalization
Hospitalization <- unlist(c(data[ace == 1, .(sum(hospital))], data[ace == 0, .(sum(hospital))], data[beta.blocker == 1, .(sum(hospital))], data[beta.blocker == 0, .(sum(hospital))], data[statin == 1, .(sum(hospital))], data[statin == 0, .(sum(hospital))]))

Variables <- c("With Ace", "Without Ace", "With BB", "Without BB", "With Statin", "Without Statin")
medicationsummary <- data.table(Variables, Death, Heart_Attack, Hospitalization)
datatable(medicationsummary)
```


####Question 6
```{r}
#Total person-years
data[, .(round((sum(end - begin))/365.25, 1))]
#Average Per Person
data[, .(round((sum(end - begin))/365.25/10000, 1))]
```


####Question 7
```{r}
#Ace
acetime <- unlist(data[ace == 1, .(round((sum(end - begin))/365.25, 1))])
offace <- unlist(data[ace == 0, .(round((sum(end - begin))/365.25, 1))])
#BB
bbtime <- unlist(data[beta.blocker == 1, .(round((sum(end - begin))/365.25, 1))])
offbb <- unlist(data[beta.blocker == 0, .(round((sum(end - begin))/365.25, 1))])
#Statin
statintime <- unlist(data[statin == 1, .(round((sum(end - begin))/365.25, 1))])
offstatin <- unlist(data[statin == 0, .(round((sum(end - begin))/365.25, 1))])


Time <- c(acetime, bbtime, statintime)
OffTime <- c(offace, offbb, offstatin)
MedicationTime <- c("Ace", "Beta Blocker", "Statin")
medicationtotal <- data.table(MedicationTime, Time, OffTime)
datatable(medicationtotal)

#Missing Time
sum(data[, .(max(end)), id][[2]]) - data[, .(sum(end - begin))]
```
No time was missing from observation

####Question 8
```{r}
#Overall follow up time 
Total_Time <- unlist(data[, .(round((sum(end - begin))/365.25, 1))])
#Each outcome
Event_Outcome <- unlist(c(data[heart.attack == 1, .N], data[death == 1, .N], data[, .(sum(diff(hospital) > 0))]))
#Ratio
Crude_Rate <- round(Event_Outcome / Total_Time * 100, 1)

vname <- c("Heart Attack", "Death", "Hospitalization")

Crude_Event_Rate <- data.table(vname, Total_Time, Event_Outcome, Crude_Rate)
datatable(Crude_Event_Rate)
```


####Question 9
```{r}
#Number of Hospitalization Events
Hospitalization_Outcome <- unlist(c(data[ace == 1, .(sum(diff(hospital) > 0))], data[ace == 0, .(sum(diff(hospital) > 0))], data[beta.blocker == 1, .(sum(diff(hospital) > 0))], data[beta.blocker == 0, .(sum(diff(hospital) > 0))], data[statin == 1, .(sum(diff(hospital) > 0))], data[statin == 0, .(sum(diff(hospital) > 0))]))
#Hospitalization Rate
htime<- unlist(c(data[ace == 1, .((sum(end - begin))/365.25)], data[ace == 0, .((sum(end - begin))/365.25)], data[beta.blocker == 1, .((sum(end - begin))/365.25)], data[beta.blocker == 0, .((sum(end - begin))/365.25)], data[statin == 1, .((sum(end - begin))/365.25)], data[statin == 0, .((sum(end - begin))/365.25)]))
Hospitalization_Rate <- round(100 * Hospitalization_Outcome / htime, 1)

#Number of Heart Attack Events
Heart_Attack_Outcome <- unlist(c(data[ace == 1, .(sum(heart.attack))], data[ace == 0, .(sum(heart.attack))], data[beta.blocker == 1, .(sum(heart.attack))], data[beta.blocker == 0, .(sum(heart.attack))], data[statin == 1, .(sum(heart.attack))], data[statin == 0, .(sum(heart.attack))]))
#Heart Attack Rate
Heart_Attack_Rate <- round(100 * Heart_Attack_Outcome / htime, 1)

#Number of Death
Death_Outcome <- unlist(c(data[ace == 1, .(sum(death))], data[ace == 0, .(sum(death))], data[beta.blocker == 1, .(sum(death))], data[beta.blocker == 0, .(sum(death))], data[statin == 1, .(sum(death))], data[statin == 0, .(sum(death))]))

#Death Rate
Death_Rate <- round(100 * Death_Outcome / htime, 1)

Variables <- c("With Ace", "Without Ace", "With BB", "Without BB", "With Statin", "Without Statin")
Medication_Usage <- data.table(Variables, Hospitalization_Outcome, Hospitalization_Rate, Heart_Attack_Outcome, Heart_Attack_Rate, Death_Outcome, Death_Rate)
datatable(Medication_Usage)
```


####Question 10
```{r}
#Hospitalization OR
Hospitalization_OR <- round(c(Hospitalization_Rate[1] / Hospitalization_Rate[2], Hospitalization_Rate[3] / Hospitalization_Rate[4], Hospitalization_Rate[5] / Hospitalization_Rate[6]), 2)

#Heart Attack OR
Heart_Attack_OR <- round(c(Heart_Attack_Rate[1] / Heart_Attack_Rate[2], Heart_Attack_Rate[3] / Heart_Attack_Rate[4], Heart_Attack_Rate[5] / Heart_Attack_Rate[6]), 2)
  
#Death OR
Death_OR <- round(c(Death_Rate[1] / Death_Rate[2], Death_Rate[3] / Death_Rate[4], Death_Rate[5] / Death_Rate[6]), 2)

Variable_Name <- c("With Ace", " With BB", "With Statin")
OddsRatio <- data.table(Variable_Name, Hospitalization_OR, Heart_Attack_OR, Death_OR)
datatable(OddsRatio)
```

